HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-12 draft/ms_v1.tex
Comments: Ono-san on other synpipe applications

%% ------------------------------------------------------------------------------------ %%
    %% Other applications
    Although we mainly focus on the general behaviors of photometric measurements here,
    \synpipe{} is quite flexible and has plenty of other applications for any HSC
    dataset.
    For instance, in a following paper, Murata\etal (in prep.) uses \synpipe{} to test
    the impacts of extremely blended objects on the WL measurements.
    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence HSC observations
    of M31 to help the search of interesting microlensing events.
    At this moment, it is also being used to help select high-$z$ Lyman-break galaxies
    and Lyman-$\alpha$ emitters (Ono\etal in prep.; Kono\etal in prep); identify
    low surface brightness dwarf galaxies (Greco\etal in prep); and test photometric
    and WL measurements around nearby clusters (Chiu\etal in prep).

>>>>

%% ------------------------------------------------------------------------------------ %%
    %% Other applications
    Although we mainly focus on the general behaviors of photometric measurements here,
    \synpipe{} is quite flexible and has plenty of other applications for any HSC
    dataset.
    For instance, in a following paper, Murata\etal (in prep.) uses \synpipe{} to test
    the impacts of extremely blended objects on the WL measurements.
    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence HSC observations
    of M31 to help the search of interesting microlensing events.
    At this moment, it is also being used to estimate the completeness of the selections 
    for high-$z$ Lyman-break galaxies (LBG) and Lyman- $\alpha$ emitters 
    (Ono\etal in prep.; Konno\etal in prep), check the dependence of the detection and 
    completeness of high-$z$ LBG pairs on the pair separation (Harikane\etal in prep.),
    identify low surface brightness dwarf galaxies (Greco\etal in prep),
    and test photometric and WL measurements around nearby clusters (Chiu\etal in prep).
